---
title: \vspace{-1.5cm} "Final report- group C"
output: pdf_document
geometry: margin=0.3cm
editor_options: 
  markdown: 
    wrap: 60
---

```{r load-packages, message=FALSE, include=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(htmltools)
library(devtools)
library(lmtest)
library(caret)
library(tidymodels)
library(tseries)
library(forecast)
library(reshape2)

```

\vspace{-1cm}

```{r setup, include = FALSE}
opts_chunk$set(echo=FALSE) # hide source code in the document
```

## Link to Code and Data

<https://github.com/FreddieMG/R-project/upload>

## Introduction

Refugees are people who have fled war, violence, conflict or
persecution and have crossed an international border to find
safety in another country.

Refugee migration has been happening for many years. Many
countries treat refugees in various ways (legislation,
treatment, becoming citizens, etc.), the refugees migration
have impact on social and political climate.

In "The Political Impact of Refugee Migration: Evidence from
the Italian Dispersal Policy" the authors find a significant
effect of the share of asylum seekers on right-wing-populist
support, contrastly, in "Do Refugees Impact Voting Behavior
in the Host Country? Evidence from Syrian Refugee Inflows in
Turkey" the authors find strong polarization in attitudes
towards refugee but no significant impact on election
outcomes. Additionaly, in the IFO DICE report "Did the
Refugee Crisis Contribute to the Recent Rise of Far-right
Parties in Europe?" the author also found support for the
far right parties increased due to the refugee crisis, but
that this could be negated by interaction between the
country's population and the refugees.
Overall, we've found that there's no clear answer to the
effects of the refugee migration into Europe, so our
research question is:

How does the change in the number of refugees affect the
political climate, specifically polarization, indicated by
support for radical parties in European countries?

Our study examines whether there is a connection between the
number of refugees and the increase in support of radical
parties both right and left. In addition we statistically
study and isolate the variables from time in order to find
the causality without of outer effect of trend, and we
explore the origin of the refugees to see if it has any
additional effect.

Contribution: Aside from contributing to a better
understanding of the social and political impact of refugee
immigration, the analysis may also assist policymakers in
deciding how to handle the refugee crisis and preparing for
its effects.

Approach : This question requires data about incoming
refugees, as well as election results of radical political
parties, and data about the population of each country.
We've used this data with multiple statistical analysis to
find the relationships between the variables.

## Data Overview

```{r include=FALSE}
polarization = read.csv('../data/Polarization.csv')
```

[**Table 1-Polarization**]{.underline}: Contains the amount
of votes received by anti-establishment (radical) parties in
each elections in each country in our representative sample.
Source: whogoverns.eu

[Columns:]{.underline} country, year- year of election,
pervote- percent of vote received by radical parties.

```{r include=FALSE}
refugees = read.csv('../data/Refugees.csv')
```

[**Table 2- Refugees**]{.underline}: Contains data about
incoming refugees and asylum seekers (we will refer to
asylum seekers as refugees as well). Source: UNHCR

[Columns:]{.underline} Year, origin- Country of origin of
the refugees, continent - continent of origin country,
asylum - country of asylum reached by the refugees,
asylum_ISO - country code for asylum country. refugees -
amount of refugees, asylum_seekers- amount of asylum
seekers.

```{r include=FALSE}
population = read.csv('../data/Population.csv')
```

[**Table 3- Population**]{.underline}: Contains data about
populations of the different countries. Source: UN.

Columns: Country, year, population.

## Methods and Results

**Data Engineering**

1.  Create total arrivals from refugees + asylum seekers
2.  Filter years from 1968 onwards due to constraints of
    election data.
3.  Group by asylum country, year.
4.  Create additional columns of amount of arrivals
    originating from each continent.
5.  Considering that we predict that election results will
    be affected by the number of incoming refugees in the
    years leading up to the election as well as in the year
    of the election, we have added cumulative columns that
    include the number of incoming refugees during this year
    as well as the 2 years prior.
6.  Since the amount of incoming refugees can impact
    countries with different population sizes differently,
    we've created columns that show the cumulative amount of
    incoming refugees as a percent of the total population.

```{r include=FALSE}
polarization <- filter(polarization, year>=1968)
```

```{r message=FALSE, include=FALSE}
aggregated_asylum <- refugees %>%
  filter(asylum_ISO%in%c('FRA', 'DEU', 'AUT', 'SWE', 'BEL','DNK', 'GRC', 'ITA', 'ESP', 'HUN'), Year>=1968) %>%
  group_by(Year, asylum_ISO) %>%
  summarise(Refugees = sum(Refugees), asylum_seekers = sum(asylum_seekers)) %>%
  mutate(total_arrivals = Refugees + asylum_seekers)


refugees_from_europe <- refugees %>%
  filter(asylum_ISO%in%c('FRA', 'DEU', 'AUT', 'SWE', 'BEL','DNK', 'GRC', 'ITA', 'ESP', 'HUN'), Year>=1968, continent == 'Europe') %>%
  group_by(Year, asylum_ISO) %>%
  summarise(Refugees = sum(Refugees), asylum_seekers = sum(asylum_seekers)) %>%
  mutate(europian_refugees = Refugees + asylum_seekers) %>%
  select(europian_refugees, Year, asylum_ISO )

refugees_from_africa <- refugees %>%
  filter(asylum_ISO%in%c('FRA', 'DEU', 'AUT', 'SWE', 'BEL','DNK', 'GRC', 'ITA', 'ESP', 'HUN'), Year>=1968, continent == 'Africa') %>%
  group_by(Year, asylum_ISO) %>%
  summarise(Refugees = sum(Refugees), asylum_seekers = sum(asylum_seekers)) %>%
  mutate(african_refugees = Refugees + asylum_seekers) %>%
  select(african_refugees, Year, asylum_ISO )

refugees_from_asia <- refugees %>%
  filter(asylum_ISO%in%c('FRA', 'DEU', 'AUT', 'SWE', 'BEL','DNK', 'GRC', 'ITA', 'ESP', 'HUN'), Year>=1968, continent == 'Asia') %>%
  group_by(Year, asylum_ISO) %>%
  summarise(Refugees = sum(Refugees), asylum_seekers = sum(asylum_seekers)) %>%
  mutate(asian_refugees = Refugees + asylum_seekers) %>%
  select(asian_refugees, Year, asylum_ISO )

refugees_from_oceania <- refugees %>%
  filter(asylum_ISO%in%c('FRA', 'DEU', 'AUT', 'SWE', 'BEL','DNK', 'GRC', 'ITA', 'ESP', 'HUN'), Year>=1968, continent == 'Oceania') %>%
  group_by(Year, asylum_ISO) %>%
  summarise(Refugees = sum(Refugees), asylum_seekers = sum(asylum_seekers)) %>%
  mutate(oceanian_refugees = Refugees + asylum_seekers) %>%
  select(oceanian_refugees, Year, asylum_ISO )

refugees_from_americas <- refugees %>%
  filter(asylum_ISO%in%c('FRA', 'DEU', 'AUT', 'SWE', 'BEL','DNK', 'GRC', 'ITA', 'ESP', 'HUN'), Year>=1968, continent == 'Americas') %>%
  group_by(Year, asylum_ISO) %>%
  summarise(Refugees = sum(Refugees), asylum_seekers = sum(asylum_seekers)) %>%
  mutate(american_refugees = Refugees + asylum_seekers) %>%
  select(american_refugees, Year, asylum_ISO )

refugees_from_stateless <- refugees %>%
  filter(asylum_ISO%in%c('FRA', 'DEU', 'AUT', 'SWE', 'BEL','DNK', 'GRC', 'ITA', 'ESP', 'HUN'), Year>=1968, continent == 'Stateless') %>%
  group_by(Year, asylum_ISO) %>%
  summarise(Refugees = sum(Refugees), asylum_seekers = sum(asylum_seekers)) %>%
  mutate(stateless_refugees = Refugees + asylum_seekers) %>%
  select(stateless_refugees, Year, asylum_ISO)

```

```{r include=FALSE}


aggregated_asylum <- merge(aggregated_asylum, refugees_from_europe, by = c("Year", "asylum_ISO")  ,all.x = TRUE)
aggregated_asylum <- merge(aggregated_asylum, refugees_from_africa, by = c("Year", "asylum_ISO")  ,all.x = TRUE)
aggregated_asylum <- merge(aggregated_asylum, refugees_from_asia, by = c("Year", "asylum_ISO")  ,all.x = TRUE)
aggregated_asylum <- merge(aggregated_asylum, refugees_from_americas, by = c("Year", "asylum_ISO")  ,all.x = TRUE)
aggregated_asylum <- merge(aggregated_asylum, refugees_from_stateless, by = c("Year", "asylum_ISO")  ,all.x = TRUE)
aggregated_asylum[is.na(aggregated_asylum)] = 0
aggregated_asylum

```

```{r include=FALSE}
# percent refugee from each continent
aggregated_asylum <- aggregated_asylum %>%
        mutate(percent_american_refugees = (american_refugees/total_arrivals)*100, percent_europian_refugees = (europian_refugees/total_arrivals)*100,
               percent_asian_refugees = (asian_refugees/total_arrivals)*100, percent_stateless_refugees = (stateless_refugees/total_arrivals)*100,
                percent_african_refugees = (african_refugees/total_arrivals)*100)

aggregated_asylum

```

```{r}
# agr_arrivals_all = c()
# cur_sum = 0
# j = 1
# maxx = length(yearly_arrivals_all_2021)
# for (year in relevant_years_all){
#   for (i in 1:maxx){
#     if (between(year-yearly_arrivals_all_2021[i], 0, 2)){
#       cur_sum = cur_sum + arrival_amount_all[i]
#     }
#     if (yearly_arrivals_all_2021[i] > year){
#       agr_arrivals_all = append(agr_arrivals_all, cur_sum)
#       cur_sum = 0
#       break
#     }
#   }
# }
# agr_arrivals_all = append(agr_arrivals_all, cur_sum)
# print(cor.test(agr_arrivals_all, pervote_all, method="pearson"))
```

```{r include=FALSE}
add_2_previous_years <- function(Row) {
  year <- strtoi(Row[1])
  country_iso <- Row[2]
 
  if (year < 1970) {
    return (0)
  }
 
(
  filter(aggregated_asylum, asylum_ISO == country_iso, Year == year)[[5]]
  +
  filter(aggregated_asylum, asylum_ISO == country_iso, Year == year-1)[[5]]
  +
  filter(aggregated_asylum, asylum_ISO == country_iso, Year == year-2)[[5]])[1]
}


# print(apply(aggregated_asylum, 1, add_2_previous_years ))

aggregated_asylum$cumulative_refugees <- apply(aggregated_asylum, 1, add_2_previous_years )
aggregated_asylum[is.na(aggregated_asylum)] = 0
```

```{r include=FALSE}
add_2_previous_years_europe <- function(Row) {
  year <- strtoi(Row[1])
  country_iso <- Row[2]
 
  if (year < 1970) {
    return (0)
  }
 
(filter(aggregated_asylum, asylum_ISO == country_iso, Year == year)[[6]]
  +
  filter(aggregated_asylum, asylum_ISO == country_iso, Year == year-1)[[6]]
  +
  filter(aggregated_asylum, asylum_ISO == country_iso, Year == year-2)[[6]])[1]
}
aggregated_asylum$cumulative_europian_refugees <- apply(aggregated_asylum, 1, add_2_previous_years_europe )
aggregated_asylum[is.na(aggregated_asylum)] = 0
```

```{r include=FALSE}
add_2_previous_years_africa <- function(Row) {
  year <- strtoi(Row[1])
  country_iso <- Row[2]
 
  if (year < 1970) {
    return (0)
  }
 
(filter(aggregated_asylum, asylum_ISO == country_iso, Year == year)[[7]]
  +
  filter(aggregated_asylum, asylum_ISO == country_iso, Year == year-1)[[7]]
  +
filter(aggregated_asylum, asylum_ISO == country_iso, Year == year-2)[[7]])[1]
}


aggregated_asylum$cumulative_african_refugees <- apply(aggregated_asylum, 1, add_2_previous_years_africa )
aggregated_asylum[is.na(aggregated_asylum)] = 0



add_2_previous_years_asia <- function(Row) {
  year <- strtoi(Row[1])
  country_iso <- Row[2]
 
  if (year < 1970) {
    return (0)
  }
 
(filter(aggregated_asylum, asylum_ISO == country_iso, Year == year)[[8]]
  +
  filter(aggregated_asylum, asylum_ISO == country_iso, Year == year-1)[[8]]
  +
filter(aggregated_asylum, asylum_ISO == country_iso, Year == year-2)[[8]])[1]
}


aggregated_asylum$cumulative_asian_refugees <- apply(aggregated_asylum, 1, add_2_previous_years_asia )
aggregated_asylum[is.na(aggregated_asylum)] = 0


add_2_previous_years_america <- function(Row) {
  year <- strtoi(Row[1])
  country_iso <- Row[2]
 
  if (year < 1970) {
    return (0)
  }
 
(filter(aggregated_asylum, asylum_ISO == country_iso, Year == year)[[9]]
  +
  filter(aggregated_asylum, asylum_ISO == country_iso, Year == year-1)[[9]]
  +
filter(aggregated_asylum, asylum_ISO == country_iso, Year == year-2)[[9]])[1]
}


aggregated_asylum$cumulative_american_refugees <- apply(aggregated_asylum, 1, add_2_previous_years_america )
aggregated_asylum[is.na(aggregated_asylum)] = 0



add_2_previous_years_stateless <- function(Row) {
  year <- strtoi(Row[1])
  country_iso <- Row[2]
 
  if (year < 1970) {
    return (0)
  }
 
(filter(aggregated_asylum, asylum_ISO == country_iso, Year == year)[[10]]
  +
  filter(aggregated_asylum, asylum_ISO == country_iso, Year == year-1)[[10]]
  +
filter(aggregated_asylum, asylum_ISO == country_iso, Year == year-2)[[10]])[1]
}


aggregated_asylum$cumulative_stateless_refugees <- apply(aggregated_asylum, 1, add_2_previous_years_stateless )
aggregated_asylum[is.na(aggregated_asylum)] = 0
```

```{r include=FALSE}
polarization<-polarization %>%
  mutate(asylum_ISO = case_when(
    country == "France" ~ "FRA",
     country == "Sweden" ~ "SWE",
     country == "Germany" ~ "DEU",
     country == "Austria" ~ "AUT",
     country == "Italy" ~ "ITA",
     country == "Belgium" ~ "BEL",
     country == "Spain" ~ "ESP",
     country == "Hungary" ~ "HUN",
     country == "Denmark" ~ "DNK",
     country == "Greece" ~ "GRC"
   
  ))%>%
  rename (Year = year)
```

```{r include=FALSE}
data = merge(x= aggregated_asylum ,y=polarization, by = c("Year","asylum_ISO"))
data
data_for_graphs = merge(x= aggregated_asylum ,y=polarization, by = c("Year","asylum_ISO"), all.x=TRUE)
```

```{r include=FALSE}
data <- merge( x = population , y = data , by.x = c("year","country_ISO"), by.y = c("Year","asylum_ISO"))
data
data_for_graphs = merge( x = population , y = data_for_graphs , by.x = c("year","country_ISO"), by.y = c("Year","asylum_ISO"))
```

```{r include=FALSE}
normalized_data <- data %>%
mutate(percent_refugee = (total_arrivals/population)*100,
       percent_cumulative = (cumulative_refugees/population)*100)

normalized_for_graphs <- data_for_graphs %>%
mutate(percent_refugee = (total_arrivals/population)*100,
       percent_cumulative = (cumulative_refugees/population)*100) %>%
  filter(year >= 1970)


normalized_for_graphs_year <- normalized_for_graphs %>%
  group_by(year) %>%
  summarise(total_arrivals = sum(total_arrivals), american_refugees = sum(american_refugees), europian_refugees=sum(europian_refugees),
            stateless_refugees=sum(stateless_refugees), asian_refugees=sum(asian_refugees),
            african_refugees = sum(african_refugees), population = sum(population), pervote = mean(pervote, na.rm = TRUE))  %>%
    mutate(Percent_american_refugees = (american_refugees/population)*100, Percent_europian_refugees = (europian_refugees/population)*100,
               Percent_stateless_refugees = (stateless_refugees/population)*100, Percent_asian_refugees = (asian_refugees/population)*100,
               Percent_african_refugees = (african_refugees/population)*100, percent_refugee = (total_arrivals/population)*100)    


normalized_data <- normalized_data %>%
                      filter(year >= 1970)

normalized_data <- normalized_data %>%
      mutate(
      percent_cumulative_europian_refugees = (cumulative_europian_refugees/population)*100,
      percent_cumulative_african_refugees = (cumulative_african_refugees/population)*100,
      percent_cumulative_asian_refugees = (cumulative_asian_refugees/population)*100,
      percent_cumulative_american_refugees = (cumulative_europian_refugees/population)*100,
      percent_cumulative_stateless_refugees = (cumulative_stateless_refugees/population)*100
      )

normalized_data
normalized_for_graphs_year
normalized_data_4 = filter(normalized_for_graphs, country_ISO%in%c('AUT', 'SWE', 'DEU', 'DNK'))

```

**Initial Visualizations:**

We've made visualizations of the data from several countries
separately and from an aggregate of the 10 countries, to try
and see if there's a connection between the percent of
radical votes and the number of incoming refugees in the
years prior to the vote:

```{r fig.height=4, fig.width=8, warning=FALSE}
ggplot(data = normalized_data_4, aes(x=year),fig(30,4)) +
  geom_bar(stat="identity", orientation = "x",
           mapping=aes(x=year, y= pervote, Justification='vote', color = "Precent of vote"), fill='bisque3')+
 geom_line(mapping=aes(y=percent_refugee*5, lty='Refugee arrivals'), color = 'deepskyblue', size=1)+
  scale_y_continuous(
    # Features of the first axis
    name = "Refugee arrivals", labels = function(x)x/5,
   
    # Add a second axis and specify its features
    sec.axis = sec_axis(~.*1, name="Precent of Vote to Radical Parties")
  )+
labs(
    color = 'Refugee Arrivals',
    title = "Number of Arriving Refugees (as Percent of Population)&
    Precent of Vote to Radical Political Parties",
    subtitle = "Divided by Country",
    caption = 'sources: UNHCR & whogoverns.eu',
    )+
  xlab('Year')+
  guides(size = FALSE)+
  theme(legend.title=element_blank(), panel.grid = element_line(linetype = 'solid', color = 'gray'), panel.background = element_rect(fill='white', colour='black'))+
  facet_wrap(~country_ISO, ncol=2, scales='free')
```

```{r fig.height=4, fig.width=8, warning=FALSE}

normalized_for_graphs_year_temp <- normalized_for_graphs_year %>%
                                  select(year,Percent_asian_refugees, Percent_europian_refugees,
                                         Percent_american_refugees, Percent_stateless_refugees,
                                         percent_refugee, Percent_african_refugees ) %>%
                                  mutate_all(~.*40) %>%
                                  mutate(year = year/40)

                                         

df = melt(normalized_for_graphs_year_temp, id.vars = "year", variable.name = "series")

ggplot(df, aes(year, value)) +
    geom_bar(stat="identity", orientation = "x",
           mapping=aes(x=year, y= pervote, Justification='vote', color = "Precent of vote"), fill='bisque3',color = "black" , data=normalized_for_graphs_year)+
  geom_line(aes(colour = series), size = 2)+


  scale_y_continuous(
    # Features of the first axis
    name = "Refugee arrivals", labels = function(x)x/25,

    # Add a second axis and specify its features
    sec.axis = sec_axis(~.*1, name="Precent of Vote to Radical Parties")
  )+
labs(
    color = 'Refugee Arrivals',
    title = "Number of Arriving Refugees (as Percent of Population)&
    Precent of Vote to Radical Political Parties",
    subtitle = "Aggregate of 10 Countries",
    caption = 'sources: UNHCR & whogoverns.eu',
    )+
  xlab('Year')+
  guides(size = FALSE)+
  theme(legend.title=element_blank(), panel.grid = element_line(linetype = 'solid', color = 'gray'), panel.background = element_rect(fill='white', colour='black'))

```

Seemingly, there is correlation between the number of
incoming refugees and the amount of votes received by
radical parties, at least in some countries and in the
aggregated graph.

We checked for Pearson correlation between the variables,
for each country and for the aggregate: 4 out of 10
countries have clear positive correlation (p_value \< 0.05).
Austria: P_value = 0.0045, cor = 0.67; Germany: P_value =
0.02, cor = 0.61; Belgium: P_value = 0.0003, cor = 0.8;
Sweden: P_value = 0.025, cor = 0.57;Aggregate: P_value =
1.561e-05 , cor = 0.560354 ;

```{r include=FALSE}
countries_dataframe_arr<-split(normalized_data, normalized_data$country_ISO)
```

```{r  include=FALSE}


check_correlation <- function(country_data){

print(country_data[1, "country_ISO"])
cor.test(country_data$pervote, country_data$percent_cumulative, method="pearson")

}
map(countries_dataframe_arr, check_correlation )

```

```{r  include=FALSE}
aggregated_Radical_votes <- polarization %>%
  group_by(Year) %>%
  # summarise(pervote = mean(pervote), vote_diff=mean(vote_diff))
  summarise(pervote = mean(pervote))
# all_votes <- filter(all_votes, year>=1970)
all_votes = filter(aggregated_Radical_votes, Year>1968)
pervote_all = pull(all_votes, pervote)
aggregated_asylum_year <- aggregated_asylum%>%
                        filter(Year >= 1970)%>%
                        group_by(Year) %>%
                        summarise(   total_arrivals= mean(total_arrivals) , cumulative_refugees = mean(cumulative_refugees))
print(length(pervote_all))
print(length(aggregated_asylum_year$cumulative_refugees))
print(cor.test(pervote_all, aggregated_asylum_year$cumulative_refugees, method="pearson"))
```

We then checked for Granger-causality in the countries that
showed correlation and received the following P values:

Austria: 0.37; Germany: = 0.5; Belgium: 0.07; Sweden: 0.69;
Aggregate: 0.41

```{r include=FALSE}


check_causation <- function(country_data){

print(country_data[1, "country_ISO"])

pervote = country_data$pervote
per_refugees = country_data$percent_cumulative
grangertest(pervote[1:length(pervote)-1]~per_refugees[2:length(per_refugees)], order=1)

}
map(countries_dataframe_arr, check_causation)

```

```{r include=FALSE}
normalized_data_per_year = normalized_data %>%
  filter(1968 <= year, year <= 2021) %>%
  group_by(year) %>%
  summarise(pervote = mean(pervote), percent_cumulative = mean(percent_cumulative),
            cumulative_refugees = mean(cumulative_refugees), percent_refugee = mean(percent_refugee),
            total_arrivals = mean(total_arrivals))
pervote = normalized_data_per_year$pervote
per_refugees = normalized_data_per_year$percent_cumulative
grangertest(pervote[1:length(pervote)-1]~per_refugees[2:length(per_refugees)], order=1)
```

These results indicate that the cumulative percent of
incoming refugees does not Granger-cause a change in the
percent of votes received by radical parties in any of the
countries.

However, since the Granger-test (and other linear
relationships between variables) can be negatively affected
if there is a trend in the data, we checked if both
variables show a trend that depends on time, which is a
recommended practice when calculating statistical data on
time-series. We've performed the Augmented Dickey--Fuller
test, and the KPSS test and the results showed a need to
detrend our data.

```{r include=FALSE}
# Check if time series are stationary
for (ISO in distinct(normalized_data, country_ISO)[[1]]){
  print(ISO)
  ISO_normalized <- normalized_data %>%
    filter(country_ISO==ISO)
  print('pervotes:')
  print(adf.test(ISO_normalized$pervote))
  print(kpss.test(ISO_normalized$pervote))
  
  print(ndiffs(ISO_normalized$pervote))
  print('arrivals:')
  print(adf.test(ISO_normalized$cumulative_refugees))
  print(kpss.test(ISO_normalized$cumulative_refugees))
  print(ndiffs(ISO_normalized$cumulative_refugees))

}
```

```{r include=FALSE}
# Check if time series are stationary

print('pervotes:')
print(adf.test(normalized_data$pervote))
print(kpss.test(normalized_data$pervote))

print(ndiffs(normalized_data$pervote))
print('arrivals:')
print(adf.test(normalized_data$cumulative_refugees))
print(kpss.test(normalized_data$cumulative_refugees))
print(ndiffs(normalized_data$cumulative_refugees))

```

We then detrended our data, which means we've calculated
regression lines for percent refugees and percent of radical
votes with the explaining variables being the year, and then
calculated the residuals from the expected values.

```{r include=FALSE}

normalized_for_graphs_year

percent_cumulative = normalized_data$percent_cumulative
percent_trend = lm(percent_cumulative~normalized_data$year)
percent_cumulative_detrended = residuals(percent_trend)


cur_pervotes = normalized_data$pervote
pervotes_trend = lm(cur_pervotes~normalized_data$year, na.action="na.exclude")
pervotes_detrended = residuals(pervotes_trend)

normalized_for_graphs_year

percent_refugee = normalized_for_graphs_year$percent_refugee
percent_trend = lm(percent_refugee~normalized_for_graphs_year$year)
normalized_for_graphs_year$percent_refugee_detrended = residuals(percent_trend)


cur_pervotes = normalized_for_graphs_year$pervote
pervotes_trend = lm(cur_pervotes~normalized_for_graphs_year$year, na.action="na.exclude")
normalized_for_graphs_year$pervotes_detrended = residuals(pervotes_trend)


Percent_asian_refugees = normalized_for_graphs_year$Percent_asian_refugees
percent_trend = lm(Percent_asian_refugees~normalized_for_graphs_year$year)
normalized_for_graphs_year$Percent_asian_refugees_detrended = residuals(percent_trend)

Percent_europian_refugees = normalized_for_graphs_year$Percent_europian_refugees
percent_trend = lm(Percent_europian_refugees~normalized_for_graphs_year$year)
normalized_for_graphs_year$Percent_europian_refugees_detrended = residuals(percent_trend)

Percent_american_refugees = normalized_for_graphs_year$Percent_american_refugees
percent_trend = lm(Percent_american_refugees~normalized_for_graphs_year$year)
normalized_for_graphs_year$Percent_american_refugees_detrended = residuals(percent_trend)

Percent_stateless_refugees = normalized_for_graphs_year$Percent_stateless_refugees
percent_trend = lm(Percent_stateless_refugees~normalized_for_graphs_year$year)
normalized_for_graphs_year$Percent_stateless_refugees_detrended = residuals(percent_trend)

Percent_african_refugees = normalized_for_graphs_year$Percent_african_refugees
percent_trend = lm(Percent_african_refugees~normalized_for_graphs_year$year)
normalized_for_graphs_year$Percent_african_refugees_detrended = residuals(percent_trend)


normalized_for_graphs_year_temp <- normalized_for_graphs_year %>%
                                  select(year,Percent_asian_refugees_detrended, Percent_europian_refugees_detrended,
                                         Percent_american_refugees_detrended, Percent_stateless_refugees_detrended,
                                         percent_refugee_detrended, Percent_african_refugees_detrended ) %>%
                                  mutate_all(~.*40) %>%
                                  mutate(year = year/40)
           

                             

df = melt(normalized_for_graphs_year_temp, id.vars = "year", variable.name = "series")

```

This is the same plot as earlier, now using detrended data:

```{r echo=FALSE, fig.height=4, fig.width=8, warning=FALSE}

ggplot(df, aes(year, value)) +
    geom_bar(stat="identity", orientation = "x",
           mapping=aes(x=year, y= pervotes_detrended, Justification='vote', color = "Precent of vote"), fill='bisque3',color = "black" , data=normalized_for_graphs_year)+
  geom_line(aes(colour = series), size = 1.5)+


  scale_y_continuous(
    # Features of the first axis
    name = "Refugee arrivals", labels = function(x)x/25,

    # Add a second axis and specify its features
    sec.axis = sec_axis(~.*1, name="Precent of Vote to Radical Parties")
  )+
labs(
    color = 'Refugee Arrivals',
    title = "Number of Arriving Refugees (as Percent of Population)&
    Precent of Vote to Radical Political Parties",
    subtitle = "aggregate of 10 Countries",
    caption = 'sources: UNHCR & whogoverns.eu',
    )+
  xlab('Year')+
  guides(size = FALSE)+
  theme(legend.title=element_blank(), panel.grid = element_line(linetype = 'solid', color = 'gray'), panel.background = element_rect(fill='white', colour='black'))


```

We then checked the correlations in each country, but the
results were not significant and the correlation results
were inconclusive. However, when looking at the aggregate,
we got a negative correlation of -0.24 with very high
confidence level: P value = 0.013.

```{r include=FALSE}
for (ISO in (distinct(normalized_data, country_ISO)[[1]])){
  print(ISO)
  ISO_normalized <- normalized_data %>%
    filter(country_ISO==ISO)
  cur_pervotes = ISO_normalized$pervote
  pervotes_trend = lm(cur_pervotes~ISO_normalized$year)
  cur_arrivals = ISO_normalized$cumulative_refugees
  arrivals_trend = lm(cur_arrivals~ISO_normalized$year)
  pervotes_detrended = residuals(pervotes_trend)
  arrivals_detrended = residuals(arrivals_trend)
  print(mean(ISO_normalized$percent_cumulative))
  print(cor.test(arrivals_detrended,pervotes_detrended, method="pearson"))
}
print('Aggregate')
cur_pervotes = normalized_data$pervote
pervotes_trend = lm(cur_pervotes~normalized_data$year)
percent_cumulative = normalized_data$percent_cumulative
percent_cumulative_trend = lm(percent_cumulative~normalized_data$year)
pervotes_detrended = residuals(pervotes_trend)
percent_cumulative_detrended = residuals(percent_cumulative_trend)
print(mean(normalized_data$percent_cumulative))
print(cor.test(percent_cumulative_detrended,pervotes_detrended, method="pearson"))
print(grangertest(pervotes_detrended[1:length(pervotes_detrended)-1]~percent_cumulative_detrended[2:length(percent_cumulative_detrended)]))

```

Additionally, we checked if the correlation of the change in
votes for radical parties was different when looking at the
number of refugees arriving from different continents. To
our surprise, even though most of the results were not at a
high confidence level, the center of the correlation's
confidence interval was very similar for all continents
(-0.06 to -0.17). We have built models that used the data of
origin continent of the refugees but ultimately the
explained variance of these features was very similar to
total amount of refugees and therefore had a high P value,
so we didn't use them in the regression.

```{r include=FALSE}

cur_percent_cumulative_europian_refugees = normalized_data$percent_cumulative_europian_refugees
percent_cumulative_europian_refugees_trend = lm(cur_percent_cumulative_europian_refugees~normalized_data$year)
percent_cumulative_europian_refugees_detrended = residuals(percent_cumulative_europian_refugees_trend)


cur_percent_cumulative_african_refugees = normalized_data$percent_cumulative_african_refugees
percent_cumulative_african_refugees_trend = lm(cur_percent_cumulative_african_refugees~normalized_data$year)
percent_cumulative_african_refugees_detrended = residuals(percent_cumulative_african_refugees_trend)

cur_percent_cumulative_asia_refugees = normalized_data$percent_cumulative_asian_refugees
percent_cumulative_asia_refugees_trend = lm(cur_percent_cumulative_asia_refugees~normalized_data$year)
percent_cumulative_asia_refugees_detrended = residuals(percent_cumulative_asia_refugees_trend)

cur_percent_cumulative_america_refugees = normalized_data$percent_cumulative_american_refugees
percent_cumulative_america_refugees_trend = lm(cur_percent_cumulative_america_refugees~normalized_data$year)
percent_cumulative_america_refugees_detrended = residuals(percent_cumulative_america_refugees_trend)

cur_percent_cumulative_stateless_refugees = normalized_data$percent_cumulative_stateless_refugees
percent_cumulative_stateless_refugees_trend = lm(cur_percent_cumulative_stateless_refugees~normalized_data$year)
percent_cumulative_stateless_refugees_detrended = residuals(percent_cumulative_stateless_refugees_trend)


print(cor.test(pervotes_detrended, percent_cumulative_europian_refugees_detrended, method="pearson"))
print(cor.test(pervotes_detrended, percent_cumulative_african_refugees_detrended, method="pearson"))
print(cor.test(pervotes_detrended, percent_cumulative_asia_refugees_detrended, method="pearson"))
print(cor.test(pervotes_detrended, percent_cumulative_america_refugees_detrended, method="pearson"))
print(cor.test(pervotes_detrended, percent_cumulative_stateless_refugees_detrended, method="pearson"))
```

We trained a linear regression model, in order to find how
well the percent of arriving refugees assists in prediction
of the percent of votes to radical parties.

```{r include=FALSE}
plot(percent_cumulative_detrended, pervotes_detrended, pch = 10, cex = 1.3  )

basic <- lm(pervotes_detrended~percent_cumulative_detrended )
sm <- summary(basic)
print(sm)
abline(basic, col = "red")
```

## Conclusions

After our initial exploration of the data, it seemed there
is positive correlation between the polarization in the
country and the amount of refugees that entered it in prior
years.

After detrending, and removing the effect of time on both
variables, which we to be significant, we see that there is
in fact causality in the opposite directions.

This means, to our surprise, that our main finding is that
an increase to the amount of incoming refugees reduces the
support to radical political parties.

The R-squared shows that this can explain about 5% of the
election results, which is a small but not insignificant
amount.

An additional conclusion we can draw, although with less
certainty, is that it seems the origin of incoming refugees
does not change the observed effects.

## Future work

-   Look more in depth into each country, try to build
    regression models for them.

-   Separate right and left wing parties to see the effects
    on each one.
